---
title: "Comparing the Effect of Ozone Levels on Temperature by Month in New York City"
author: "J.E. Panzik"
date: "6/16/2020"
output: ioslides_presentation
---

## Key Questions
- Does ozone level appear to impact the measured temperature?
- If present, does the does this pattern vary by month?

### Interactive Shiny App
- App:
    - <https://jepanzik.shinyapps.io/DDP_CourseProject_ShinyApp/>
- Source Code:
    - <https://github.com/jepanzik/Coursera-Developing-Data-Products-Week-4-Project/tree/master/DDP_CourseProject_ShinyApp>


## Plotting code

```{r plotcode, eval=FALSE, message=FALSE, warning=FALSE}
library(ggplot2); library(gridExtra)
data <- airquality[complete.cases(airquality),]
data$Month <- as.factor(data$Month)
p1 <- ggplot(data=data, aes(x=Ozone, y=Temp)) +
      geom_point(aes(color=Month)) + xlab("Ozone (ppb)") +
      ylab("Temperature (F)") + ylim(55, 100) +
      xlim(0, 170) + geom_smooth(method='lm')

p2 <- ggplot(data=data, aes(x=Ozone, y=Temp, color=Month)) +
      geom_point() + xlab("Ozone (ppb)") + ylab("Temperature (F)") +
      ylim(55, 100) + xlim(0, 170) + geom_smooth(method='lm')

grid.arrange(p1, p2, ncol=2)
```

## Plots

```{r plot, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2); library(gridExtra)
data <- airquality[complete.cases(airquality),]
data$Month <- as.factor(data$Month)
p1 <- ggplot(data=data, aes(x=Ozone, y=Temp)) +
      geom_point(aes(color=Month)) + xlab("Ozone (ppb)") +
      ylab("Temperature (F)") + ylim(55, 100) +
      xlim(0, 170) + geom_smooth(method='lm')

p2 <- ggplot(data=data, aes(x=Ozone, y=Temp, color=Month)) +
      geom_point() + xlab("Ozone (ppb)") + ylab("Temperature (F)") +
      ylim(55, 100) + xlim(0, 170) + geom_smooth(method='lm')

grid.arrange(p1, p2, ncol=2)
```

## Conclusions
- Based on the plots created, it **DOES** appear that ozone has an impact on the measured temperature.
- There is a variation in the impact ozone has on temperature based on month.
    - The hottest months (July & August) appear to not be impacted as much by increases in ozone.